Appendix S1: Supporting Tables and Figures.

### 2022-07-29 ms/SI.Rmd
update for copy-edit
- punch -> disc
- errors in table S2
- add csv for S1
- add doi

Summary of a linear mixed model for log-transformed total dry mass of leaf discs for each tree individual.
Species was used as a random intercept.
The leaf punch size is described as an effect of '0.6 cm diameter' compared with '1.0 cm diameter'.

@@

::: {.center data-latex=""}
![](../figs/S2.jpeg){ width=470 margin=auto }
:::

>>>>

Summary of a linear mixed model for log-transformed total dry mass of leaf discs for each tree individual.
Species was used as a random intercept.
The small disc is described as an effect of '0.6 cm diameter' compared with '1.0 cm diameter'.

@@

::: {.center data-latex=""}
![](../figs/s1.jpeg){ width=470 margin=auto }
:::

### 2022-07-29 ms/SI.tex
update for copy-edit
- punch -> disc
- errors in table S2
- add csv for S1
- add doi

Summary of a linear mixed model for log-transformed total dry mass of leaf discs for each tree individual.
Species was used as a random intercept.
The leaf punch size is described as an effect of `0.6 cm diameter' compared with `1.0 cm diameter'.

\begin{table}[H]
\centering
\begin{tabular}[t]{rrrrl}
\toprule
Estimate & SE & DF & t-value & \textit{P} value\\
\midrule
\cellcolor{gray!6}{-4.410} & \cellcolor{gray!6}{0.013} & \cellcolor{gray!6}{1030} & \cellcolor{gray!6}{-333.00} & \cellcolor{gray!6}{< 0.001}\\
0.240 & 0.007 & 1030 & 33.20 & < 0.001\\
\cellcolor{gray!6}{-0.061} & \cellcolor{gray!6}{0.009} & \cellcolor{gray!6}{1030} & \cellcolor{gray!6}{-6.94} & \cellcolor{gray!6}{< 0.001}\\
0.277 & 0.008 & 1030 & 34.90 & < 0.001\\
\cellcolor{gray!6}{-0.500} & \cellcolor{gray!6}{0.020} & \cellcolor{gray!6}{332} & \cellcolor{gray!6}{-25.60} & \cellcolor{gray!6}{< 0.001}\\
\bottomrule
\end{tabular}
\end{table}

@@

\begin{center}
\includegraphics[width=4.89583in,height=\textheight]{../figs/S2.jpeg}

>>>>

Summary of a linear mixed model for log-transformed total dry mass of leaf discs for each tree individual.
Species was used as a random intercept.
The small disc is described as an effect of `0.6 cm diameter' compared with `1.0 cm diameter'.

\begin{table}[H]
\centering
\begin{tabular}[t]{lrrrrl}
\toprule
Predictors & Estimate & SE & DF & t-value & \textit{P} value\\
\midrule
\cellcolor{gray!6}{(Intercept)} & \cellcolor{gray!6}{-4.410} & \cellcolor{gray!6}{0.013} & \cellcolor{gray!6}{1030} & \cellcolor{gray!6}{-333.00} & \cellcolor{gray!6}{< 0.001}\\
log(Leaf tissue density) & 0.240 & 0.007 & 1030 & 33.20 & < 0.001\\
\cellcolor{gray!6}{log(Leaf area)} & \cellcolor{gray!6}{-0.061} & \cellcolor{gray!6}{0.009} & \cellcolor{gray!6}{1030} & \cellcolor{gray!6}{-6.94} & \cellcolor{gray!6}{< 0.001}\\
log(Leaf thickness) & 0.277 & 0.008 & 1030 & 34.90 & < 0.001\\
\cellcolor{gray!6}{Small disc} & \cellcolor{gray!6}{-0.500} & \cellcolor{gray!6}{0.020} & \cellcolor{gray!6}{332} & \cellcolor{gray!6}{-25.60} & \cellcolor{gray!6}{< 0.001}\\
\bottomrule
\end{tabular}
\end{table}

@@

\begin{center}
\includegraphics[width=4.89583in,height=\textheight]{../figs/s1.jpeg}
